---
# Mixed Models: General Case 

Consider the Linear Regression with $m$ marketing activities and $i$ regions:

\begin{equation}
Y_{it} = \beta_0 + \sum_{j=0}^{m} \beta_{j} X_{ijt} + \sum_{j=0}^{m} \beta^{(i)}_{j} X_{ijt}  + \varepsilon_{it}
\end{equation}

where: 

* $t$ is a unit of time (eg. week, month, etc)
* $Y_{it}$ is the KPI of interest (eg. Sales in Chicago in March)
* $X_j$ is the marketing spend for the $j$th marketing variable (eg. TV ads, Youtube Ads, Google Ads, etc)
* $\beta_j$ is the average incremental effect of one unit of $X_{jt}$
* $\beta^{(i)}_j$ is the deviation from the average incremental effect of one unit of $X_{jt}$ in region $i$
* $\varepsilon_{it}$ is the modelling error, i.e difference between predicted and actual values of the KPI

---
class: font130
# Interpreting Mixed Models

Consider an example from the 2 marketing activity $\times$ 2 region model:

* $\hat{\beta}_1 = 0.5$, $\hat{\beta}_2 = 0.75$
* $\hat{\beta}^{\text{Chicago}}_1 = 0.5$, $\hat{\beta}^{\text{Chicago}}_2 = 0.25$
* $\hat{\beta}^{\text{SanFran}}_1 = -0.25$, $\hat{\beta}^{\text{SanFran}}_2 = -0.5$

What do these estimates mean?


In class ...

---
# A Two Activity, Two Region Mixed Model

Suppose only spend on Facedb Ads and TV Ads, KPI is Sales.

Two Regions: National data, want different effects for Chicago and San Francisco.

Form a regression model:

\begin{align}
\text{Sales}_{it} = \beta_0 &+ \underbrace{\beta_{1F} \text{YouTube Ad Spending}_{it} + \beta_{2F} \text{TV Ad Spending}_{it}}_{\text{Average Impacts}} \\
                            &+ \underbrace{\beta_{1\text{Chicago}} \text{YouTube Ad Spending}_{it} + \beta_{2\text{Chicago}} \text{TV Ad Spending}_{it}}_{\text{Chicago's Deviations}} \\
                            &+ \underbrace{\beta_{1\text{San Fran}} \text{YouTube Ad Spending}_{it} + \beta_{2\text{San Fran}} \text{TV Ad Spending}_{it}}_{San Franciso's Deviations} \\
                            &+ \varepsilon_{it}
\end{align}

Then: 

* Average Impacts: $\beta_{jF}$
* Chicago Impacts: $\beta_{jF}$ + $\beta_{j\text{Chicago}}$
* San Franciso Impacts: $\beta_{jF}$ + $\beta_{j\text{San Franciso}}$ 


---
class: inverse, center, middle

# Detour: Linear Regression Modelling

---
# Example: Orange Juice

```{r, echo = FALSE, fig.align = "center", out.width="70%"}
url <- "https://parade.com/.image/t_share/MTkwNTgwODY0NjExMTk4MDc3/is-orange-juice-good-for-you-jpg.jpg"
knitr::include_graphics(url)
```

* Three Brands: Tropicana, Minute Maid and Dominicks 
* 83 Chicagoland Stores 
* Data on price, sales (quantity) and whether promoted
* Want to know the price elasticity of demand. How does this change when on promotion?

```{r, echo = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(broom)

oj <- read_csv("data/oj.csv")
```

---
# The Data: A Glimpse

```{r, echo = FALSE}
head(oj, n = 10)
```

---
# The Juice: Price, Brand and Sales 

.pull-left[
```{r, echo = FALSE}
oj %>%
  ggplot() +
  geom_boxplot(
    aes(x = brand, y = price, fill = brand)
  ) +
  theme_bw()
```
]

.pull-right[
```{r, echo = FALSE}
oj %>%
  ggplot() +
  geom_point(
    aes(x = log(sales/1e3), y = log(price), color = brand),
    alpha = 0.5
  ) +
  theme_bw()
```

]

.center[**Each brand occupies a well defined price range. Sales decrease with price**]

---
# Simple Linear Regression 

$$Sales_i = \beta_0 + \beta_1 price_i + \varepsilon_i$$

Remark: Sales in '000s.

```{r, echo = FALSE}
summary(lm(sales/1e3 ~ price, data = oj))
```

---
# Visualizing the Regression Line

```{r, echo = FALSE}
oj %>%
  ggplot() +
  geom_point(
    aes(x = log(sales/1e3), y = log(price), color = brand),
    alpha = 0.5
  ) +
  geom_smooth(method = "lm",
              aes(x = log(sales/1e3), y = log(price)),
              color = "black",
              alpha = 0.75
              ) +
  xlab("quantity") + 
  ylab("price") +
  theme_bw()
```

---
class: font150
# Simple Linear Regression: Explaining

Discussion Questions:

* Why is this regression line the "right" one?

* Can we explain each part of the statistical output?

* How to interpret the regression coefficients?

* Does our regression line have any important properties?

* Is price the only variable that contributes to demand? 

* What are the implications of "omitted variables"?

---
# Logarithmic Transformations I

$$\log(Sales)_i = \beta_0 + \beta_1 price_i + \varepsilon_i$$

```{r, echo = FALSE}
tidy(lm(log(sales) ~ price, data = oj))
```

**Coefficient Interpretation** (in general): 

On average, a change in X by one unit, $\Delta X=1$, is associated with a $(\exp(\beta_1) - 1)*100$ % change in Y

* Remark: for small $\beta_1$, $(\exp(\beta_1) - 1) \approx \beta_1$ so often you will see an interpretation that reads straight from $\beta_1$ 

**Coefficient Interpretation** (this example): 

---
# Logarithmic Transformations II

$$\log(Sales)_i = \beta_0 + \beta_1 \log(price_i) + \varepsilon_i$$

```{r, echo = FALSE}
tidy(lm(log(sales) ~ log(price), data = oj))
```

**Coefficient Interpretation** (in general): 

On average, a 1% change in X is associated with a change in $\beta_1$ % change in Y 
  * $\beta_1$ is the elasticity of Y with respect to X

**Coefficient Interpretation** (this example): 

---
class: inverse, center, middle
# Multivariable Regression 

---
# Multivariable Regression: One Control

$$Sales_i = \beta_0 + \beta_1 price_i + \beta_2 \text{feat}_i + \varepsilon_i$$

Remark: Sales in '000s.

```{r, echo = FALSE}
summary(lm(sales ~ price + feat, data = oj))
```

---
class: font150
# Multiple Linear Regression: Explaining

Discussion Questions:

* Can we explain each part of the statistical output?

* How to interpret the regression coefficients?

* Was price the only variable that contributes to demand? 

* What are the implications of "omitted variables"?

---
# Multivariable Regression: One Control II

$$\log(Sales)_i = \beta_0 + \beta_1 \log(price_i) + \beta_2 \text{feat}_i + \varepsilon_i$$

```{r, echo = FALSE}
summary(lm(log(sales) ~ log(price) + feat, data = oj))
```

---
# Multivariable Regression: Many Controls

$$
\begin{aligned}
\log(Sales)_i = \beta_0 &+ \beta_1 \log(price_i) + \beta_2 \text{feat}_i + \\ 
                        &\beta_3 \text{Tropicana}_i  + \beta_4 \text{Minute Maid}_i + \varepsilon_i
\end{aligned}
$$

```{r, echo = FALSE}
summary(lm(log(sales) ~ log(price) + feat + brand, data = oj))
```

---
class: clear

```{r, echo = FALSE, fig.align = "center", out.width="100%"}
url <- "figs/mainevent.gif"
knitr::include_graphics(url)
```


